---
title: "p8105_hw5_wq2160"
author: "Wenshan Qu (wq2160)"
date: "11/19/2021"
output: github_document
---

```{r include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Raw data

```{r}
homicide_df = 
  read_csv("./data/homicides/homicide-data.csv", na = c("", "Unknown"))
```

Describe: There are `r nrow(homicide_df)` rows and `r ncol(homicide_df)` columns in this dataset, and key variables including `r names(homicide_df)``.

1. _Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”)._

```{r}
homicide_df = 
  homicide_df %>% 
  mutate(
    city_state = str_c(city, state, sep = ","),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "Tulsa,AL")

homicide_df
```

2. _For the city of `Baltimore, MD`, use the `prop.test` function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the `broom::tidy` to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe._

```{r}
baltimore_df = 
  homicide_df %>% 
    filter(city_state == "Baltimore,MD")

baltimore_summary = 
  baltimore_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"), ## get the number of unsolved cases
      n = n()
    )
  
baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
  )

baltimore_test %>% 
  broom::tidy()
```

3. _Now run `prop.test` for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of `purrr::map`, `purrr::map2`, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city._

Write a function:

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
      summarize(
        unsolved = sum(resolution == "unsolved"), 
        n = n()
      )
    
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  
  return(city_test)

}
```

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
    ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

4. _Create a plot that shows the estimates and CIs for each city – check out `geom_errorbar` for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides._

```{r}
results_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Alternative way to get same results...using `map2()`

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```
